---
title: "SURVEY SAMPLING TECHNIQUES- “METU Students’ Habits of Using Online Education Platforms"
author: "AyşegülBinbaş"
date: "20 12 2020"
output: word_document
---
```{r}
library(readxl)
data<-read_excel("data.xlsx")
head(data)
```
colnames(data)<-c("time","e-mail","gender","age","faculty","grade","using_online_edc","which_are_most_used","how_often","what_purpose","for_which_field","payoff","how_much_money_spent","satisfaction_from_spent_money","what_differs_from_others","satisfaction_of_platforms","want_to_add_smth")
head(data)
library(ggplot2)
table(data$gender)
data1<- data.frame(
  gender=c("Male","Female","PanSexual","TransSexual"),  
  count=c(42,56,1,1)
  )
ggplot(data1, aes(x=gender, y=count)) + 
  geom_bar(stat = "identity",fill="red",colour="black")+
  ggtitle("Bar Plot of Gender")+
  geom_text(aes(label=count), vjust=-0.3, size=3.5)+
  theme_minimal()
table(data$age)
library(plotrix)
age<-c("17-22","23-28")
freq1<-c(70,30)
percentage<-round(freq1/sum(freq1)*100)
labels_new<-paste(age,' ',percentage)
labels_new
final_labels<-paste(labels_new,'%',sep = "")
final_labels
pie3D(freq1,labels = final_labels,explode = 0.3,main='Pie Chart of Age',labelcex = 1.8,shade = 0.5,radius = .9)
library(gcookbook)
table(data$grade)
grade<-c("Preparatory","1st grade","2nd grade","3rd grade","4th grade")
freq<-c(4,12,47,24,13)
data3<- data.frame(grade,freq)
ggplot(data3,aes(x=factor(grade),y=freq))+
  geom_bar(stat="identity",fill="blue",colour="black")+
  ggtitle("Bar Plot of Grades")
table(data$faculty)
library(plotrix)
faculty<-c("Architecture","Education","Engineering","Economics and Administrative Sciences","Arts and Science")
freq2<-c(3,9,16,23,49)
percentage<-round(freq2/sum(freq2)*100)
labels_new<-paste(faculty,' ',percentage)
labels_new
final_labels<-paste(labels_new,'%',sep = "")
final_labels
pie3D(freq2,labels = final_labels,explode = 0.2,main='Pie Chart of Faculty',labelcex =1.2,shade = 0.7,radius = .8)
dataa<-read_excel("data.xlsx")
head(dataa)
colnames(dataa)<-c("time","e-mail","gender","age","faculty","grade","using_online_edc","which_are_most_used","how_often","what_purpose","for_which_field","payoff","how_much_money_spent","satisfaction_from_spent_money","what_differs_from_others","satisfaction_of_platforms","want_to_add_smth")
#HYPO 1: There is an association between the grades of METU Students’ and using online education platforms. (Q5 & Q6)
table(dataa$grade,dataa$using_online_edc)
df<-as.data.frame(table(dataa$grade,dataa$using_online_edc))
colnames(df)<-c("Grades","Using","Frequencies")
ggplot(df,aes(x=as.factor(Using),y=Frequencies))+
  geom_bar(stat="identity",fill="blue",colour="black")+
  ggtitle("Bar Plot of Grades & Using Online Educ. Plat.")+
  facet_wrap(~Grades)
#H0: The two variables are independent.
#H1: The two variables relate to each other.
```{r}
chisq.test(table(dataa$grade, dataa$using_online_edc))
```
#HYPO 2: Female students are more tend to use online education platforms than others. (Q2 & Q6)
table(dataa$gender,dataa$using_online_edc)
chisq.test(table(dataa$gender,dataa$using_online_edc))
df<-as.data.frame(table(dataa$gender,dataa$using_online_edc))
colnames(df)<-c("Gender","Using","Frequencies")
ggplot(df,aes(x=as.factor(Using),y=Frequencies))+
  geom_bar(stat="identity",fill="chocolate",colour="black")+
  ggtitle("Bar Plot of Gender & Using Online Educ. Plat.")+
  facet_wrap(~Gender)
#hypo3: There is an association between the Faculties of students and using online education platforms. (Q4 & Q6)
table(dataa$faculty,dataa$using_online_edc)
chisq.test(table(dataa$faculty,dataa$using_online_edc))
df<-as.data.frame(table(dataa$faculty,dataa$using_online_edc))
colnames(df)<-c("Faculty","Using","Frequencies")
ggplot(df,aes(x=as.factor(Using),y=Frequencies))+
  geom_bar(stat="identity",fill="darkcyan",colour="black")+
  ggtitle("Bar Plot of Faculty & Using Online Educ. Plat.")+
  facet_wrap(~Faculty)
#Hypo 6: Students who pay fewer fees are more satisfied from online education platform they use. (Q12 & Q15)
x<-dataa$how_much_money_spent
y<-dataa$satisfaction_of_platforms
z<-dataa$using_online_edc
notusing<-which(z==2)
x<-x[-notusing]
y<-y[-notusing]
length(which(is.na(y)))
length(which(is.na(x)))
summary(y)
summary(x)
nas<-which(is.na(x))
y[17]=3
x[nas]=1
table(x,y)
chisq.test(table(x,y))
#Hypo 7:There is an association between the students’ faculties and whether or not they pay some fee for online education platforms. (Q4 & Q11)
x<- dataa$faculty
y<- dataa$payoff
z<-dataa$using_online_edc
notusing<-which(z==2)
x<-x[-notusing]
y<-y[-notusing]
length(which(is.na(y)))
length(which(is.na(x)))
summary(y)
summary(x)
nas<-which(is.na(y))
y[nas]=1
table(x,y)
chisq.test(table(x,y))
